Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-26 VMCAI-revised-version/final.tex
up

From then on, we can split $\Safe$ into two subsets: an upward-closed 
union of sets $\mathop{\uparrow} q(\textbf{0})$ and a remaining downward-closed subset.
The key now is that elements of $\Bad$ of the form $p(\textbf{v})$ with $ \textbf{v} > \textbf{v}_{\Bad}$ can only potentially reach the upward-closed subset of $\Safe$ in $k$ or less steps.
\mathieu{Write small text and refer to appendix~\ref{appendix vass}}
\qed
\end{proof}

>>>>

From then on, we partition $\Safe$ into two subsets: an upward-closed 
union of sets of the form $\mathop{\uparrow} q(\textbf{0})$, and a remaining downward-closed subset.
The key now is that
there is only a finite number of elements of $\Bad$ of the form $p(\textbf{v})$ with $ \textbf{v} \leq \textbf{u}_k$ for all of which we will check reachability of $\Safe$ in $k$ or less steps, while 
 elements of $\Bad$ of the form $p(\textbf{v})$ with $ \textbf{v} > \textbf{u}_k$ can only potentially reach the upward-closed subset of $\Safe$ in $k$ or less steps.
\mathieu{Write small text and refer to appendix~\ref{appendix vass}}
\qed
\end{proof}
